\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-01 papers/jfp/2-background.tex
Work on S7
Drafting changes in sections 1-3

Build systems automate the execution of repeatable tasks for individual users
and large organisations. In this section we explore the design space of build
systems, using four concrete examples: \Make~\cite{feldman1979make},
\Shake~\cite{mitchell2012shake}, \Bazel~\cite{bazel}, and
\Excel~\cite{advanced_excel}.
We have carefully chosen these four to illustrate the various axes on which
build systems differ; we discuss many other notable examples of build systems,
and their relationships, in~\S\ref{sec-implementations} and~\S\ref{sec-related}.

@@

\Make\footnote{There are numerous implementations of \Make and none comes with a
formal specification. In this paper we use a simple approximation to a real
\Make that you might find on your machine.} was developed
more than 40 years ago to automatically build software libraries and executable
programs from source code. It uses \emph{makefiles} to describe tasks, often
referred to as \emph{build rules}, and their dependencies in a simple textual
form. For example:

@@

\noindent
The above makefile lists three tasks: (i) compile a utility library comprising
files \cmd{util.h} and \cmd{util.c} into \cmd{util.o} by
executing\footnote{In this example we pretend \cmd{gcc} is a pure function for
the sake of simplicity. In reality, there are multiple versions of \cmd{gcc} and
the actual binary used to compile and link files, as well as standard libraries
such that \cmd{stdio.h}, are often also listed as dependencies.} the command
\cmd{gcc -c util.c}, (ii) compile the main source file \cmd{main.c} into
\cmd{main.o}, and (iii) link object files \cmd{util.o} and \cmd{main.o} into the
executable \cmd{main.exe}. The makefile contains the complete information about
the \emph{task dependency graph}, which is shown in Fig.~\ref{fig-make}(a).

@@

If the user runs \Make specifying \cmd{main.exe} as the desired output, \Make
will build~\cmd{util.o} and~\cmd{main.o}, in any order since these tasks are
independent, and then \cmd{main.exe}. If the user modifies \cmd{util.h} and runs
\Make again, it will perform a \emph{full rebuild}, because all three tasks
transitively depend on \cmd{util.h}, as illustrated in Fig.~\ref{fig-make}(b).
On the other hand, if the user modifies \cmd{main.c} then a \emph{partial
rebuild} is sufficient: \cmd{util.o} does not need to be rebuilt, since its
inputs have not changed, see Fig.~\ref{fig-make}(c). Note that if the dependency
graph is \emph{acyclic} then each task needs to be executed at most once. Cyclic
task dependencies are typically not allowed in build systems but there are rare
exceptions, see~\S\ref{sec-iterative-compute}.

@@

\vspace{2mm}
\textbf{Definition} (Minimality). A build system is \emph{minimal} if it
executes tasks at most once per build and only if they transitively depend on
inputs that changed since the previous build.\label{def-minimal}
\vspace{2mm}

@@

\noindent
The formula in \cmd{B1} uses the \cmd{INDIRECT} function, which takes a string
and returns the value of the cell with that name.  The string evaluates to
\cmd{"A1"}, so \cmd{B1} evaluates to \cmd{10}. However, the dependencies of the
formula in \cmd{B1} are determined by the value of \cmd{C1}, so it is impossible
to compute the dependency graph before the build starts. In this particular
example one might say that the value of \cmd{C1} is statically known, but
imagine that it is the result of a long computation chain -- its value will only
become available during the build.

@@

The dependencies of \cmd{release.tar} are not known statically: they are
determined by the content of \cmd{release.txt}, which might not even exist
before the build. Makefiles cannot express such dependencies, requiring problematic
workarounds such as \emph{build phases} \cite{hadrian}.
In \Shake we can express the rule for \cmd{release.tar} as:

@@

\Shake's implementation is different from both \Make and \Excel in two aspects.
First, it uses the dependency graph from the previous build to decide which
files need to be rebuilt. This idea has a long history, going back to
\emph{incremental}~\cite{demers1981incremental},
\emph{adaptive}~\cite{acar2002adaptive}, and
\emph{self-adjusting computations} -- see
Acar~\etal~\shortcite{acar2007selfadjusting} and~\S\ref{sec-related}. Second,
instead of aborting and deferring the execution of tasks whose newly discovered
dependencies have not yet been built (as \Excel does), \Shake \emph{suspends}
their execution until the dependencies are brought up to date. We refer to this
task scheduling algorithm as \emph{suspending}, see a concrete implementation
in~\S\ref{sec-implementation-shake}.

@@

Consider an example in Fig.~\ref{fig-bazel}. The user starts by downloading the
sources, whose content hashes are (for simplicity)~1,~2 and~3, and requests to
build \cmd{main.exe}, see Fig.~\ref{fig-bazel}(a,b). By looking up the global
history of all previous builds\footnote{In practice, old entries are regularly
evicted from the cloud storage, as further discussed
in~\S\ref{sec-cloud-aspects}.}, the build system finds that someone has already
compiled these exact sources before and the resulting files \cmd{util.o} and
\cmd{main.o} had hashes 4~and~5, respectively. Similarly, the build system finds
that the hash of the resulting \cmd{main.exe} was 6 and downloads the actual
binary from the cloud storage -- it must be materialised, because it is the end
build product.

@@

To support cloud builds, \Bazel maintains (i) a \emph{content-addressable cache}
that can be used to download a previously built file given the hash of its
content, and (ii) the history of all executed build commands annotated with
observed file hashes. The latter allows the build engine to bypass the execution
of a task, by predicting the hash of the result from the hashes of its
dependencies, and subsequently download the result from the cache. A concrete
implementation is provided in~\S\ref{sec-implementation-cloud}.

>>>>

Build systems automate the execution of repeatable tasks, at a scale from individual users
up to large organisations. In this section we explore the design space of build
systems, using four concrete examples: \Make~\cite{feldman1979make},
\Shake~\cite{mitchell2012shake}, \Bazel~\cite{bazel}, and
\Excel~\cite{advanced_excel}.
We have carefully chosen these four to illustrate the various axes on which
build systems differ; we discuss many other notable examples of build systems,
and their relationships, in~\S\ref{sec-implementations} and~\S\ref{sec-related}.

@@

\Make\footnote{There are numerous implementations of \Make and none comes with a
formal specification. In this paper we use a simple approximation to a real
\Make that you might find on your machine.} was developed
more than 40 years ago to automatically build software libraries and executable
programs from source code. It uses \emph{makefiles} to describe \emph{tasks} --- often
referred to as \emph{build rules} --- and their \emph{dependencies}, in a simple textual
form. For example:

@@

\noindent
The above makefile lists three tasks: (i) compile a utility library comprising
files \cmd{util.h} and \cmd{util.c} into \cmd{util.o} by
executing\footnote{In this example we pretend \cmd{gcc} is a pure function for
  the sake of simplicity. In reality, there are multiple versions of \cmd{gcc}.
  To account for this, the actual binary for \cmd{gcc} is often listed as a dependency, along
  with any supporting binaries, or standard libraries (such as \cmd{stdio.h}),
  that are used by \cmd{gcc}.
} the command
\cmd{gcc -c util.c}, (ii) compile the main source file \cmd{main.c} into
\cmd{main.o}, and (iii) link object files \cmd{util.o} and \cmd{main.o} into the
executable \cmd{main.exe}. The makefile contains the complete information about
the \emph{task dependency graph}, which is shown in Fig.~\ref{fig-make}(a).

@@

If the user runs \Make specifying \cmd{main.exe} as the desired output, \Make
will build~\cmd{util.o} and~\cmd{main.o}, in any order (or even in parallel) since these tasks are
independent, and then \cmd{main.exe}. If the user modifies \cmd{util.h} and runs
\Make again, it will perform a \emph{full rebuild}, because all three tasks
transitively depend on \cmd{util.h}, as illustrated in Fig.~\ref{fig-make}(b).
On the other hand, if the user modifies \cmd{main.c} then a \emph{partial
rebuild} is sufficient: \cmd{util.o} does not need to be rebuilt, since its
inputs have not changed, see Fig.~\ref{fig-make}(c). Note that if the dependency
graph is \emph{acyclic} then each task needs to be executed at most once. Cyclic
task dependencies are typically not allowed in build systems, although there are rare
exceptions, see~\S\ref{sec-iterative-compute}.

@@

\vspace{2mm}
\textbf{Definition} (Minimality). A build system is \emph{minimal} if it
executes tasks at most once per build, and only if they transitively depend on
inputs that changed since the previous build.\label{def-minimal}
\vspace{2mm}

@@

\noindent
The formula in \cmd{B1} uses the \cmd{INDIRECT} function, which takes a string
and returns the value of the cell with that name.  The string evaluates to
\cmd{"A1"}, so \cmd{B1} evaluates to \cmd{10}. However, the dependencies of the
formula in \cmd{B1} are determined by the value of \cmd{C1}, so it is impossible
to compute the dependency graph before the build starts. In this particular
example the value of \cmd{C1} is a constant, but
it might instead be the result of a long computation chain --
so its value will only
become available during the build.

@@

The dependencies of \cmd{release.tar} are not known statically: they are
determined by the content of \cmd{release.txt}, which might not even exist
before the build. Makefiles cannot express such dependencies, requiring problematic
workarounds such as \emph{build phases}~\cite{hadrian}.
In \Shake we can express the rule for \cmd{release.tar} as:

@@

\Shake's implementation is different from both \Make and \Excel in two aspects.
First, to decide which files need to be rebuilt,
it uses the dependency graph that is dynamically constructed during
the previous build . This idea has a long history, going back to
\emph{incremental}~\cite{demers1981incremental},
\emph{adaptive}~\cite{acar2002adaptive}, and
\emph{self-adjusting computations} -- see
Acar~\etal~\shortcite{acar2007selfadjusting} and~\S\ref{sec-related}. Second,
instead of aborting and deferring the execution of tasks whose newly discovered
dependencies have not yet been built (as \Excel does), \Shake \emph{suspends}
their execution until the dependencies are brought up to date. We refer to this
task scheduling algorithm as \emph{suspending}, see a concrete implementation
in~\S\ref{sec-implementation-shake}.

@@

Consider the example in Fig.~\ref{fig-bazel}. The user starts by downloading the
sources, whose content hashes are (for simplicity)~1,~2 and~3, and requests to
build \cmd{main.exe}, see Fig.~\ref{fig-bazel}(a,b). By looking up the global
history of all previous builds\footnote{In practice, old entries are regularly
evicted from the cloud storage, as further discussed
in~\S\ref{sec-cloud-aspects}.}, the build system finds that someone has already
compiled these exact sources before and the resulting files \cmd{util.o} and
\cmd{main.o} had hashes 4~and~5, respectively. Similarly, the build system finds
that the hash of the resulting \cmd{main.exe} was 6 and downloads the actual
binary from the cloud storage -- it must be materialised, because it is the end
build product.

@@

To support cloud builds, \Bazel maintains (i) a \emph{content-addressable cache}
that maps the hash of a file's content to the actual content of that file;
(ii) a memo table that records all executed build commands
with their input file hashes and output file value.
The memo table allows the build engine to bypass the execution
of a task, by predicting the hash of the result from the hashes of its
dependencies; then the content-addressable cache allows the engine
to download the result (if needed) based on the result hash. A concrete
implementation is provided in~\S\ref{sec-implementation-cloud}.

### 2019-05-01 papers/jfp/3-abstractions.tex
Drafting changes in sections 1-3

This section presents abstractions that allow us to express
all the intricacies of build systems discussed in~\S\ref{sec-background},
and express complex build systems from simple primitives. Specifically, we
present the \emph{task} and \emph{build} abstractions in~\S\ref{sec-task}
and~\S\ref{sec-general-build}, respectively. Sections~\S\ref{sec-scheduler},
\S\ref{sec-rebuilder} and~\S\ref{sec-implementations} scrutinise the
abstractions further and provide concrete implementations for several build
systems.

@@

\emph{Build system.} A \emph{build system} takes a task description, a
\emph{target} key, and a store, and returns a new store in which the target key
and all its dependencies have up to date values.

We model build systems concretely, as Haskell programs. To that end,
Fig.~\ref{fig-types} provides the type signatures for all key abstractions
introduced in the paper. For example, \hs{Store}~\hs{i}~\hs{k}~\hs{v} is the
type of stores, with several associated functions (\hs{getValue}, etc.). We use
\hs{k} as a type variable ranging over keys, \hs{v} for values, and \hs{i} for
the persistent build information. Fig.~\ref{fig-stdlib} lists standard library
definitions.

@@

\noindent
Here \hs{c} stands for \emph{constraint}, such as \hs{Applicative}
(\S\ref{sec-why-polymorphism} explains why we need it).
A \hs{Task} describes a single build task, while \hs{Tasks} associates a
\hs{Task} to every non-input key; input keys are associated with \hs{Nothing}.
The highly-abstracted type \hs{Task} describes how to build a value given
a way to build its dependencies, and is best explained by an example.
Consider this \Excel spreadsheet:
% \footnote{Readers familiar with \emph{lenses} or \emph{profunctor optics} might
% recognise a familiar pattern. We discuss this in~\S\ref{sec-related-optics}.}

@@

The code to ``compute the value of a formula'' in \hs{sprsh1} looks a bit
mysterious because it takes place in an \hs{Applicative}
computation~\cite{mcbride2008applicative} -- the relevant type signatures are
given in Fig.~\ref{fig-stdlib}. We will explain why in~\S\ref{sec-general-build}.

For now, we content ourselves with observing that a task description, of type
\hs{Tasks}~\hs{c}~\hs{k}~\hs{v}, is completely isolated from the world of
compilers, calc chains, file systems, caches, and all other complexities of real
build systems. It just computes a single output, in a side-effect-free way,
using a callback (\hs{fetch}) to find the values of its dependencies.

@@

\noindent
As we can see, \hs{busy} built both \cmd{B2} and its dependency \cmd{B1} in the
right order (if it had built \cmd{B2} before building \cmd{B1}, the result would
have been $20 * 2 = 40$ instead of $(10 + 20) * 2 = 60$). As an example showing
that \hs{busy} is not minimal, imagine that the formula in cell \cmd{B2} was
\cmd{B1~+~B1} instead of \cmd{B1~*~2}. This would lead to calling
\hs{fetch}~\hs{"B1"} twice -- once per occurrence of \cmd{B1} in the
formula.

@@

But nor can the task description work for \emph{any} \hs{f}; most task
descriptions (e.g. \hs{sprsh1} in \S\ref{sec-task}) require that \hs{f}
satisfies certain properties, such as \hs{Applicative} or \hs{Monad}. That is
why \hs{Task} has the ``\hs{c}~\hs{f}~\hs{=>}'' constraint in its type,
expressing that \hs{f} can only be instantiated by types that satisfy the
constraint \hs{c}. So the type \hs{Task} emerges naturally, almost inevitably.
But now that it \emph{has} emerged, we find that constraints \hs{c} classify
task descriptions in a very interesting way:
\begin{itemize}
\item \hs{Task}~\hs{Applicative}. In \hs{sprsh1} we needed only \hs{Applicative}
  operations, expressing the fact that the dependencies between cells can be
  determined \emph{statically}; that is, by looking at the formulae, without
  ``computing'' them (see \S\ref{sec-deps}).
\item \hs{Task}~\hs{Monad}. As we shall see in \S\ref{sec-task-monad}, a monadic
  task allows \emph{dynamic} dependencies, in which a formula may depend on cell
  \cmd{C}, but \emph{which} cell \cmd{C} depends on the value of another cell
  \cmd{D}.
\item \hs{Task}~\hs{Functor} is somewhat degenerate: a functorial task
  description cannot even use the application operator \hs{<*>}, which limits
  dependencies to a linear chain, as e.g. in Docker containers~\cite{docker}. It
  is interesting to note that, when run on such a task description, the
  \hs{busy} build system will build each key at most once, thus partially
  fulfilling the minimality requirement~\ref{def-minimal}. Alas, it still has no
  mechanism to decide which input keys changed since the previous build.
\item \hs{Task}~\hs{MonadFail} correspond to monadic tasks that may fail. For
  example, the formula \cmd{A1/A2} may fail due to division by zero. We will
  discuss this in~\S\ref{sec-failures}.
\item \hs{Task}~\hs{Alternative}, \hs{Task}~\hs{MonadPlus} and their
  variants can be used for describing tasks with a certain type of
  non-determinism, as discussed in~\S\ref{sec-non-determinism}.
\item \hs{Task}~\hs{(MonadState}~\hs{i)} will be used
  in~\S\ref{sec-implementations} to describe tasks that have read and write
  access to the persistently stored build information~\hs{i}.
\end{itemize}

@@

As explained in~\S\ref{sec-background-excel}, some task descriptions have
dynamic dependencies, which are determined by values of intermediate
computations. In our framework, such task descriptions correspond to the type
\hs{Tasks}~\hs{Monad}~\hs{k}~\hs{v}. Consider this spreadsheet example:

@@

\noindent
Here we do not need any effects in the \hs{fetch} callback to \hs{task}, so
we can use the standard Haskell \hs{Identity} monad (Fig.~\ref{fig-stdlib}).
The use of \hs{Identity} just fixes the ``impedance mismatch'' between the
function \hs{getValue}, which returns a pure value~\hs{v}, and the \hs{fetch}
argument of the \hs{task}, which must return an \hs{f}~\hs{v} for some \hs{f}.
To fix the mismatch, we wrap the result of \hs{getValue} in the \hs{Identity}
monad and pass to the \hs{task}. The result has type \hs{Identity}~\hs{v}, which
we unwrap with \hs{runIdentity}.

@@

Earlier we remarked that a \hs{Task}~\hs{Applicative} could only have static
dependencies. Usually we would extract such static dependencies by (in the case
of \Excel) looking at the syntax tree of the formula.  But a task description
has no such syntax tree. Yet, remarkably, we can use the polymorphism of a
\hs{Task}~\hs{Applicative} to find its dependencies \emph{without doing any of
the actual work}. Here is the code:

>>>>

We have introduced a number of components and
characteristics of build systems:
tasks, dependencies, early cutoff, minimality, etc.
It is easy to get confused.
To make all this more concrete, this section presents executable
abstractions that can express
all the intricacies of build systems discussed in~\S\ref{sec-background},
and allow us to construct complex build systems from simple primitives. Specifically, we
present the \emph{task} and \emph{build} abstractions in~\S\ref{sec-task}
and~\S\ref{sec-general-build}, respectively. Sections~\S\ref{sec-scheduler},
\S\ref{sec-rebuilder} and~\S\ref{sec-implementations} scrutinise the
abstractions further and provide concrete implementations for several build
systems.

@@

\emph{Build system.} A \emph{build system} takes a task description, a
\emph{target key}, and a store, and returns a new store in which the target key
and all its dependencies have up to date values.

We model a build system concretely, as a Haskell program. To that end,
Fig.~\ref{fig-types} provides the type signatures for all key abstractions
introduced in the paper. For example, \hs{Store}~\hs{i}~\hs{k}~\hs{v} is the
type of stores, with several associated functions (\hs{getValue}, etc.). We use
\hs{k} as a type variable ranging over keys, \hs{v} for values, and \hs{i} for
the persistent build information. Fig.~\ref{fig-stdlib} lists standard library
definitions.

@@

\noindent
Here \hs{c} stands for \emph{constraint}, such as \hs{Applicative}
(\S\ref{sec-why-polymorphism} explains why we need it).
A \hs{Task} describes a single build task, while \hs{Tasks} associates a
\hs{Task} with every non-input key; input keys are associated with \hs{Nothing}.
The highly-abstracted type \hs{Task} describes how to build a value given
a way to build its dependencies, and is best explained by an example.
Consider this \Excel spreadsheet:
% \footnote{Readers familiar with \emph{lenses} or \emph{profunctor optics} might
% recognise a familiar pattern. We discuss this in~\S\ref{sec-related-optics}.}

@@

The code to ``compute the value of a formula'' in \hs{sprsh1} looks a bit
mysterious because it takes place in an \hs{Applicative}
computation~\cite{mcbride2008applicative} -- the relevant type signatures are
given in Fig.~\ref{fig-stdlib}. We will explain why in~\S\ref{sec-general-build}.
For now, we content ourselves with observing that a task description, of type
\hs{Tasks}~\hs{c}~\hs{k}~\hs{v}, is completely isolated from the world of
compilers, calc chains, file systems, caches, and all other complexities of real
build systems. It just computes a single output,
using a callback (\hs{fetch}) to find the values of its dependencies,
and limiting side effects to those described by \hs{c}.

@@

\noindent
As we can see, \hs{busy} built both \cmd{B2} and its dependency \cmd{B1} in the
correct order (if it had built \cmd{B2} before building \cmd{B1}, the result would
have been $20 * 2 = 40$ instead of $(10 + 20) * 2 = 60$). As an example showing
that \hs{busy} is not minimal, imagine that the formula in cell \cmd{B2} was
\cmd{B1~+~B1} instead of \cmd{B1~*~2}. This would lead to calling
\hs{fetch}~\hs{"B1"} twice -- once per occurrence of \cmd{B1} in the
formula -- and each call would recompute the formula in \cmd{B1}.

@@

But the task description cannot possibly work for \emph{any} \hs{f} whatsoever; most task
descriptions (e.g. \hs{sprsh1} in \S\ref{sec-task}) require that \hs{f}
satisfies certain properties, such as \hs{Applicative} or \hs{Monad}. That is
why \hs{Task} has the ``\hs{c}~\hs{f}~\hs{=>}'' constraint in its type,
expressing that \hs{f} can only be instantiated by types that satisfy the
constraint \hs{c} and, in exchange, the task has access to the operations of class \hs{c}.
So the type \hs{Task} emerges naturally, almost inevitably.
But now that it \emph{has} emerged, we find that constraints \hs{c} classify
task descriptions in a very interesting, and practically useful, way:
\begin{itemize}
\item \hs{Task}~\hs{Applicative}. In \hs{sprsh1} we needed only \hs{Applicative}
  operations, expressing the fact that the dependencies between cells can be
  determined \emph{statically}; that is, by looking at the formulae, without
  ``computing'' them (see \S\ref{sec-deps}).
\item \hs{Task}~\hs{Monad}. As we shall see in \S\ref{sec-task-monad}, a monadic
  task allows \emph{dynamic} dependencies, in which a formula may depend on cell
  \cmd{C}, but \emph{which} cell \cmd{C} depends on the value of another cell
  \cmd{D}.
\item \hs{Task}~\hs{Functor} is somewhat degenerate: a functorial task
  description cannot even use the application operator \hs{<*>}, which limits
  dependencies to a linear chain, as e.g. in Docker containers~\cite{docker}. It
  is interesting to note that, when run on such a task description, the
  \hs{busy} build system will build each key at most once, thus partially
  fulfilling the minimality requirement~\ref{def-minimal}. Alas, it still has no
  mechanism to decide which input keys changed since the previous build.
\item \hs{Task}~\hs{MonadFail} correspond to monadic tasks that may fail. For
  example, the formula \cmd{A1/A2} may fail due to division by zero. We will
  discuss this in~\S\ref{sec-failures}.
\item \hs{Task}~\hs{Alternative}, \hs{Task}~\hs{MonadPlus} and their
  variants can be used for describing tasks with a certain type of
  non-determinism, as discussed in~\S\ref{sec-non-determinism}.
\item \hs{Task}~\hs{(MonadState}~\hs{i)} will be used
  in~\S\ref{sec-implementations} to describe tasks that have read and write
  access to the persistently stored build information~\hs{i}.
\end{itemize}

@@

As explained in~\S\ref{sec-background-excel}, some task descriptions have
dynamic dependencies, which are determined by values of intermediate
computations. In our framework, such task descriptions correspond to the type
\hs{Task}~\hs{Monad}~\hs{k}~\hs{v}. Consider this spreadsheet example:

@@

\noindent
Here we do not need any effects in the \hs{fetch} callback to \hs{task}, so
we can use the standard Haskell \hs{Identity} monad (Fig.~\ref{fig-stdlib}).
Here is our first use of polymorpism in \hs{f}, discussed in \S\ref{sec-why-polymorphism}.
The use of \hs{Identity} just fixes the ``impedance mismatch'' between the
function \hs{getValue}, which returns a pure value~\hs{v}, and the \hs{fetch}
argument of the \hs{task}, which must return an \hs{f}~\hs{v} for some \hs{f}.
To fix the mismatch, we wrap the result of \hs{getValue} in the \hs{Identity}
monad and pass to the \hs{task}. The result has type \hs{Identity}~\hs{v}, which
we unwrap with \hs{runIdentity}.

@@

Earlier we remarked that a \hs{Task}~\hs{Applicative} could only have static
dependencies. Usually we would extract such static dependencies by (in the case
of \Excel) looking at the syntax tree of the formula.  But a task description
has no such syntax tree: as you can see in the definition of \hs{Task} in Fig.~\ref{fig-types},
a task is just a function, so all we can do is call it.
\hs{Task}~\hs{Applicative} to find its dependencies \emph{without doing any of
the actual work}. Here is the code:
